### 2020-04-30 serial_analysis.tex
still making so many changes!!

% Created by tikzDevice version 0.12.3 on 2020-04-20 00:29:27
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,139.66) --
	( 45.69,139.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,139.66) --
	( 45.69,174.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,174.34) --
	( 45.69,174.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,114.90) --
	( 51.21,114.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,114.90) --
	( 51.21,169.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,169.39) --
	( 51.21,169.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,134.71) --
	( 56.73,134.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,134.71) --
	( 56.73,154.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.52) --
	( 56.73,154.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,104.99) --
	( 62.25,104.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,104.99) --
	( 62.25,174.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,174.34) --
	( 62.25,174.34);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,139.66) --
	( 73.29,139.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,139.66) --
	( 73.29,189.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,189.20) --
	( 73.29,189.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,134.71) --
	( 78.81,134.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,134.71) --
	( 78.81,154.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.52) --
	( 78.81,154.52);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,119.85) --
	( 89.85,119.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,119.85) --
	( 89.85,159.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,159.48) --
	( 89.85,159.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 80.22) --
	( 95.37, 80.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 80.22) --
	( 95.37,174.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,174.34) --
	( 95.37,174.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 95.08) --
	(100.89, 95.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 95.08) --
	(100.89,164.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,164.43) --
	(100.89,164.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 90.13) --
	(106.42, 90.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 90.13) --
	(106.42,149.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,149.57) --
	(106.42,149.57);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94, 85.17) --
	(111.94,159.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,159.48) --
	(111.94,159.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 90.13) --
	(117.46, 90.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 90.13) --
	(117.46,164.43);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 45.55) --
	(122.98, 45.55);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 45.55) --
	(122.98,169.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,169.39) --
	(122.98,169.39);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50, 85.17) --
	(128.50,149.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,149.57) --
	(128.50,149.57);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02, 90.13) --
	(134.02,144.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,144.62) --
	(134.02,144.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 65.36) --
	(139.54, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 65.36) --
	(139.54,134.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,134.71) --
	(139.54,134.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 60.41) --
	(145.06, 60.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 60.41) --
	(145.06,144.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,144.62) --
	(145.06,144.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 65.36) --
	(150.58, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 65.36) --
	(150.58,149.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,149.57) --
	(150.58,149.57);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10, 40.59) --
	(156.10,134.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,134.71) --
	(156.10,134.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 50.50) --
	(161.62, 50.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 50.50) --
	(161.62,129.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,129.76) --
	(161.62,129.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 60.41) --
	(167.14, 60.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 60.41) --
	(167.14,109.94);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 65.36) --
	(172.66, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 65.36) --
	(172.66,109.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,109.94) --
	(172.66,109.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 75.27) --
	(178.19, 75.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 75.27) --
	(178.19,109.94);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.17) --
	(183.71, 85.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.17) --
	(183.71,100.04);

@@

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 35.64) --
	(211.31, 35.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 35.64) --
	(211.31, 85.17);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 85.17) --
	(211.31, 85.17);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor,fill opacity=0.20] ( 34.64,171.01) --
	( 36.88,169.05) --
	( 39.12,167.14) --
	( 41.35,165.27) --
	( 43.59,163.46) --
	( 45.83,161.68) --
	( 48.06,159.96) --
	( 50.30,158.29) --
	( 52.54,156.67) --
	( 54.77,155.10) --
	( 57.01,153.59) --
	( 59.24,152.12) --
	( 61.48,150.70) --
	( 63.72,149.32) --
	( 65.95,147.97) --
	( 68.19,146.66) --
	( 70.43,145.37) --
	( 72.66,144.09) --
	( 74.90,142.81) --
	( 77.13,141.54) --
	( 79.37,140.25) --
	( 81.61,138.94) --
	( 83.84,137.61) --
	( 86.08,136.26) --
	( 88.32,134.88) --
	( 90.55,133.47) --
	( 92.79,132.04) --
	( 95.02,130.59) --
	( 97.26,129.14) --
	( 99.50,127.74) --
	(101.73,126.42) --
	(103.97,125.19) --
	(106.21,124.07) --
	(108.44,123.07) --
	(110.68,122.19) --
	(112.91,121.41) --
	(115.15,120.75) --
	(117.39,120.02) --
	(119.62,119.00) --
	(121.86,117.91) --
	(124.10,116.89) --
	(126.33,115.70) --
	(128.57,114.48) --
	(130.80,113.34) --
	(133.04,112.27) --
	(135.28,111.11) --
	(137.51,109.84) --
	(139.75,108.69) --
	(141.99,107.59) --
	(144.22,106.58) --
	(146.46,105.54) --
	(148.69,104.57) --
	(150.93,103.63) --
	(153.17,102.62) --
	(155.40,101.65) --
	(157.64,100.75) --
	(159.88, 99.93) --
	(162.11, 99.20) --
	(164.35, 98.48) --
	(166.58, 97.75) --
	(168.82, 97.00) --
	(171.06, 96.23) --
	(173.29, 95.46) --
	(175.53, 94.69) --
	(177.77, 93.95) --
	(180.00, 93.23) --
	(182.24, 92.56) --
	(184.47, 91.94) --
	(186.71, 91.37) --
	(188.95, 90.85) --
	(191.18, 90.39) --
	(193.42, 89.99) --
	(195.66, 89.64) --
	(197.89, 89.34) --
	(200.13, 89.10) --
	(202.36, 88.91) --
	(204.60, 88.77) --
	(206.84, 88.68) --
	(209.07, 88.64) --
	(211.31, 88.65) --
	(211.31, 46.93) --
	(209.07, 50.41) --
	(206.84, 53.75) --
	(204.60, 56.97) --
	(202.36, 60.04) --
	(200.13, 62.98) --
	(197.89, 65.79) --
	(195.66, 68.45) --
	(193.42, 70.97) --
	(191.18, 73.35) --
	(188.95, 75.58) --
	(186.71, 77.67) --
	(184.47, 79.62) --
	(182.24, 81.42) --
	(180.00, 83.08) --
	(177.77, 84.60) --
	(175.53, 86.01) --
	(173.29, 87.29) --
	(171.06, 88.48) --
	(168.82, 89.58) --
	(166.58, 90.59) --
	(164.35, 91.53) --
	(162.11, 92.39) --
	(159.88, 93.23) --
	(157.64, 94.16) --
	(155.40, 95.15) --
	(153.17, 96.16) --
	(150.93, 97.18) --
	(148.69, 98.28) --
	(146.46, 99.36) --
	(144.22,100.40) --
	(141.99,101.43) --
	(139.75,102.42) --
	(137.51,103.58) --
	(135.28,104.76) --
	(133.04,105.87) --
	(130.80,107.14) --
	(128.57,108.40) --
	(126.33,109.53) --
	(124.10,110.53) --
	(121.86,111.53) --
	(119.62,112.53) --
	(117.39,113.40) --
	(115.15,114.13) --
	(112.91,114.80) --
	(110.68,115.58) --
	(108.44,116.44) --
	(106.21,117.32) --
	(103.97,118.24) --
	(101.73,119.19) --
	( 99.50,120.18) --
	( 97.26,121.23) --
	( 95.02,122.36) --
	( 92.79,123.51) --
	( 90.55,124.65) --
	( 88.32,125.78) --
	( 86.08,126.91) --
	( 83.84,128.03) --
	( 81.61,129.15) --
	( 79.37,130.26) --
	( 77.13,131.35) --
	( 74.90,132.43) --
	( 72.66,133.48) --
	( 70.43,134.49) --
	( 68.19,135.47) --
	( 65.95,136.39) --
	( 63.72,137.26) --
	( 61.48,138.06) --
	( 59.24,138.79) --
	( 57.01,139.45) --
	( 54.77,140.04) --
	( 52.54,140.55) --
	( 50.30,140.98) --
	( 48.06,141.33) --
	( 45.83,141.61) --
	( 43.59,141.82) --
	( 41.35,141.95) --
	( 39.12,142.01) --
	( 36.88,142.01) --
	( 34.64,141.94) --
	cycle;

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (122.98,  7.64) {Primary cohort time (days)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (251.45,105.23) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (275.01, 47.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (280.90,110.02) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (286.79, 81.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (292.68,124.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (298.57, 90.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (304.45, 83.31) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.34, 98.52) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (316.23, 87.25) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (322.12, 95.32) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (328.01,102.53) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,105.54) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.79,106.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.68,105.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (351.57,100.32) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (357.45,107.92) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.34,112.15) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.23,113.22) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,111.54) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.01,112.98) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.90,115.62) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (392.79,121.14) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.68,124.15) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (404.56,122.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (410.45,139.38) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.34,133.19) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (422.23,167.55) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (428.12,148.37) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,105.23) --
	(251.45,105.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,105.23) --
	(251.45,105.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,105.23) --
	(251.45,105.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 47.70) --
	(275.01, 47.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 47.70) --
	(275.01, 47.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 47.70) --
	(275.01, 47.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,105.23) --
	(280.90,105.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,105.23) --
	(280.90,114.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,114.82) --
	(280.90,114.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.26) --
	(286.79, 81.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.26) --
	(286.79, 81.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.26) --
	(286.79, 81.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,124.40) --
	(292.68,124.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,124.40) --
	(292.68,124.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,124.40) --
	(292.68,124.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 90.85) --
	(298.57, 90.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 90.85) --
	(298.57, 90.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 90.85) --
	(298.57, 90.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45, 42.91) --
	(304.45, 42.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45, 42.91) --
	(304.45,138.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45,138.78) --
	(304.45,138.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 86.05) --
	(310.34, 86.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 86.05) --
	(310.34,133.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34,133.99) --
	(310.34,133.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23, 62.08) --
	(316.23, 62.08);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-04-30 02:40:57
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,173.47) --
	( 45.69,173.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,173.47) --
	( 45.69,142.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.69,142.26) --
	( 45.69,142.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,167.16) --
	( 51.21,167.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,167.16) --
	( 51.21,115.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 51.21,115.39) --
	( 51.21,115.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.03) --
	( 56.73,154.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,154.03) --
	( 56.73,135.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 56.73,135.21) --
	( 56.73,135.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,173.35) --
	( 62.25,173.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,173.35) --
	( 62.25,107.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.25,107.47) --
	( 62.25,107.47);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,187.96) --
	( 73.29,187.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,187.96) --
	( 73.29,140.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.29,140.90) --
	( 73.29,140.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.03) --
	( 78.81,154.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,154.03) --
	( 78.81,135.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.81,135.21) --
	( 78.81,135.21);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,158.36) --
	( 89.85,158.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,158.36) --
	( 89.85,120.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.85,120.22) --
	( 89.85,120.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,168.89) --
	( 95.37,168.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37,168.89) --
	( 95.37, 85.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.37, 85.67) --
	( 95.37, 85.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,157.00) --
	(100.89,157.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89,157.00) --
	(100.89, 96.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.89, 96.94) --
	(100.89, 96.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,147.34) --
	(106.42,147.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42,147.34) --
	(106.42, 94.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.42, 94.59) --
	(106.42, 94.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,156.63) --
	(111.94,156.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.94,156.63) --
	(111.94, 85.17);

@@

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46,164.43) --
	(117.46, 94.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.46, 94.22) --
	(117.46, 94.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,163.56) --
	(122.98,163.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98,163.56) --
	(122.98, 72.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.98, 72.91) --
	(122.98, 72.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,142.39) --
	(128.50,142.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.50,142.39) --
	(128.50, 85.17);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,141.52) --
	(134.02,141.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.02,141.52) --
	(134.02, 90.13);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,125.30) --
	(139.54,125.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54,125.30) --
	(139.54, 70.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.54, 70.07) --
	(139.54, 70.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,143.75) --
	(145.06,143.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06,143.75) --
	(145.06, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.06, 65.36) --
	(145.06, 65.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,135.45) --
	(150.58,135.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58,135.45) --
	(150.58, 70.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.58, 70.07) --
	(150.58, 70.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,129.26) --
	(156.10,129.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.10,129.26) --
	(156.10, 40.59);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,125.79) --
	(161.62,125.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62,125.79) --
	(161.62, 58.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.62, 58.43) --
	(161.62, 58.43);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14,109.94) --
	(167.14, 64.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (167.14, 64.37) --
	(167.14, 64.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,107.96) --
	(172.66,107.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66,107.96) --
	(172.66, 73.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.66, 73.29) --
	(172.66, 73.29);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19,109.94) --
	(178.19, 77.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.19, 77.74) --
	(178.19, 77.74);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71,100.04) --
	(183.71, 85.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (183.71, 85.67) --
	(183.71, 85.67);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 83.94) --
	(211.31, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 83.94) --
	(211.31, 36.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.31, 36.88) --
	(211.31, 36.88);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (122.98,  7.64) {Symptom onset day (infector)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (251.45,108.69) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (275.01, 43.54) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (280.90,114.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (286.79, 81.54) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (292.68,130.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (298.57, 92.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (304.45, 83.87) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.34,101.09) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (316.23, 88.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (322.12, 97.47) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (328.01,105.63) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (333.90,109.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.79,110.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.68,109.44) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (351.57,103.13) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (357.45,111.73) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.34,116.53) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.23,117.73) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,115.83) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.01,117.47) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.90,120.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (392.79,126.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (398.68,130.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (404.56,128.31) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (410.45,147.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.34,140.35) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (422.23,179.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (428.12,157.54) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,108.69) --
	(251.45,108.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,108.69) --
	(251.45,108.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.45,108.69) --
	(251.45,108.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 43.54) --
	(275.01, 43.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 43.54) --
	(275.01, 43.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (275.01, 43.54) --
	(275.01, 43.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,119.27) --
	(280.90,119.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,119.27) --
	(280.90,108.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.90,108.96) --
	(280.90,108.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.54) --
	(286.79, 81.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.54) --
	(286.79, 81.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (286.79, 81.54) --
	(286.79, 81.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,130.40) --
	(292.68,130.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,130.40) --
	(292.68,130.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.68,130.40) --
	(292.68,130.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 92.40) --
	(298.57, 92.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 92.40) --
	(298.57, 92.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (298.57, 92.40) --
	(298.57, 92.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45,139.36) --
	(304.45,139.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45,139.36) --
	(304.45, 38.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (304.45, 38.12) --
	(304.45, 38.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34,136.92) --
	(310.34,136.92);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34,136.92) --
	(310.34, 86.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.34, 86.97) --
	(310.34, 86.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23,107.74) --
	(316.23,107.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (316.23,107.74) --
	(316.23, 60.78);
